---
title: "World Governance Network"
---

## Introduction

The World Governance Network is derived from World Bank data on governance indicators.For now, we are focusing on high-income countries.


## World Governance Indicators

The following governance indicators were taken into account when compiling these networks:

1.  Voice & Accountability

2.  Political Stability and Lack of Violence

3.  Government Effectiveness

4.  Regulatory Quality

5.  Rule of Law

6.  Control of Corruption

## Data

Below is a link to the data.

<https://databank.worldbank.org/source/worldwide-governance-indicators>

## R Codes for World Governance Clustering

```R
#| warning: false
library(tidyverse)
library(networkD3)
library(visNetwork)
library(igraph)
gov <- read.csv("C:/Users/user/Desktop/WGN/WorldGN/high_income.csv",
                row.names=1)
gov <- na.omit(gov)
hc <- hclust(dist(gov),"ave")
dendroNetwork(hc,
              height = 6000,
              width = 4000#,treeOrientation="vertical"
              )

rad <- as.radialNetwork(hc, '')
radialNetwork(List = rad,
              height = 4000,
              width = 4000,
              fontSize = 8)

gdist<- as.matrix(dist(gov,
                       method = "euclidean",
                       diag = FALSE,
                       upper = FALSE,
                       p = 2))
gnet <- graph_from_adjacency_matrix(
  gdist,
  mode ="undirected",
  weighted = TRUE,
  diag = TRUE,
  add.colnames = NULL,
  add.rownames = NA
)
gmst<- mst(gnet)
data <- toVisNetworkData(gmst)
visNetwork(nodes = data$nodes, edges = data$edges, height = "1000px",fontSize = 16)
```


## High-Income Countries

```{r}
#| warning: false
#| echo: false
library(tidyverse)
library(networkD3)
library(visNetwork)
library(igraph)
gov <- read.csv("C:/Users/user/Desktop/WGN/WorldGN/high_income.csv",
                row.names=1)
gov <- na.omit(gov)
hc <- hclust(dist(gov),"ave")
dendroNetwork(hc,
              height = 6000,
              width = 4000#,treeOrientation="vertical"
              )

rad <- as.radialNetwork(hc, '')
radialNetwork(List = rad,
              height = 4000,
              width = 4000,
              fontSize = 8)


gdist<- as.matrix(dist(gov,
                       method = "euclidean",
                       diag = FALSE,
                       upper = FALSE,
                       p = 2))
gnet <- graph_from_adjacency_matrix(
  gdist,
  mode ="undirected",
  weighted = TRUE,
  diag = TRUE,
  add.colnames = NULL,
  add.rownames = NA
)
gmst<- mst(gnet)
data <- toVisNetworkData(gmst)
visNetwork(nodes = data$nodes, edges = data$edges, height = "1000px",fontSize = 16)
```

## Upper-Middle-Income Countries

```{r}
#| warning: false
#| echo: false
library(tidyverse)
library(networkD3)
library(visNetwork)
library(igraph)
gov <- read.csv("C:/Users/user/Desktop/WGN/WorldGN/upper_middle_income.csv",
                row.names=1)
gov <- na.omit(gov)
hc <- hclust(dist(gov),"ave")
dendroNetwork(hc,
              height = 6000,
              width = 4000#,treeOrientation="vertical"
              )

rad <- as.radialNetwork(hc, '')
radialNetwork(List = rad,
              height = 4000,
              width = 4000,
              fontSize = 8)


gdist<- as.matrix(dist(gov,
                       method = "euclidean",
                       diag = FALSE,
                       upper = FALSE,
                       p = 2))
gnet <- graph_from_adjacency_matrix(
  gdist,
  mode ="undirected",
  weighted = TRUE,
  diag = TRUE,
  add.colnames = NULL,
  add.rownames = NA
)
gmst<- mst(gnet)
data <- toVisNetworkData(gmst)
visNetwork(nodes = data$nodes, edges = data$edges, height = "1000px",fontSize = 16)
```

## Lower-Middle-Income Countries

```{r}
#| warning: false
#| echo: false
library(tidyverse)
library(networkD3)
library(visNetwork)
library(igraph)
gov <- read.csv("C:/Users/user/Desktop/WGN/WorldGN/lower_middle_income.csv",
                row.names=1)
gov <- na.omit(gov)
hc <- hclust(dist(gov),"ave")
dendroNetwork(hc,
              height = 6000,
              width = 4000#,treeOrientation="vertical"
              )

rad <- as.radialNetwork(hc, '')
radialNetwork(List = rad,
              height = 4000,
              width = 4000,
              fontSize = 8)


gdist<- as.matrix(dist(gov,
                       method = "euclidean",
                       diag = FALSE,
                       upper = FALSE,
                       p = 2))
gnet <- graph_from_adjacency_matrix(
  gdist,
  mode ="undirected",
  weighted = TRUE,
  diag = TRUE,
  add.colnames = NULL,
  add.rownames = NA
)
gmst<- mst(gnet)
data <- toVisNetworkData(gmst)
visNetwork(nodes = data$nodes, edges = data$edges, height = "1000px",fontSize = 16)
```

## Low-Income Countries

```{r}
#| warning: false
#| echo: false
library(tidyverse)
library(networkD3)
library(visNetwork)
library(igraph)
gov <- read.csv("C:/Users/user/Desktop/WGN/WorldGN/low_income.csv",
                row.names=1)
gov <- na.omit(gov)
hc <- hclust(dist(gov),"ave")
dendroNetwork(hc,
              height = 6000,
              width = 4000#,treeOrientation="vertical"
              )

rad <- as.radialNetwork(hc, '')
radialNetwork(List = rad,
              height = 4000,
              width = 4000,
              fontSize = 8)


gdist<- as.matrix(dist(gov,
                       method = "euclidean",
                       diag = FALSE,
                       upper = FALSE,
                       p = 2))
gnet <- graph_from_adjacency_matrix(
  gdist,
  mode ="undirected",
  weighted = TRUE,
  diag = TRUE,
  add.colnames = NULL,
  add.rownames = NA
)
gmst<- mst(gnet)
data <- toVisNetworkData(gmst)
visNetwork(nodes = data$nodes, edges = data$edges, height = "1000px",fontSize = 16)
```
